Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-28 lloveras_2020_Albert.tex
Nuevo texto de PHIs por Albert

\albert{For both rotations it is readily seen that the integrated radiative loss, measured by the quantity $\phi_r$, is largest for loops of type 0, smaller for loops of type I, and smallest for loops of type II . This is mainly due to the fact that in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. Indeed, according to Table 1, loops of type 0 have the lowest temperature of them all and closest to $\Tc$, for both rotations.}

@@

\albert{The characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.0 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop. These values are similar to those reported by \citet{maccormack_2017}.}

>>>>

\albert{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II. This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors cooperating to maximize $E_r$ for loops of type 0 and minimize it for loops of type II. As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0, I and II are characterised by progressively decreasing electron density for both rotations. Also, in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by progressively larger electron temperature, and progressively farther from the value $\Tc$, for both rotations.}

@@

\albert{As a result of the radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of loop. These values are similar to those reported by \citet{maccormack_2017}.}
